BioTime

### 2019-10-03 data-raw/amphibio.Rmd
Make function for resolving multiple trait entries to one id, resolve for elton database as well.
Standardize trait column names, simplify trait matrix column selection.

```{r}
library(tidyverse)

@@

amph <- read_csv(system.file("extdata", "amphibio/AmphiBIO_v1.csv", package = "biodivTS"))

amphibio <- amph %>%
  mutate(id = get_ids(Species, "itis")) %>%
  filter(!is.na(id)) %>%
  mutate(scientificName = get_names(id, "itis")) %>%
  select(id, scientificName, Species) %>%
  right_join(select(amph, -id), by = "Species") %>%
  rename(sourceName = Species) %>%
  select(-c("Order", "Family", "Genus"))

@@

>>>>

```{r}
library(tidyverse)
library(taxadb)

@@

amph <- read_csv(system.file("extdata", "amphibio/AmphiBIO_v1.csv", package = "biodivTS")) %>%
  rename_all(tolower) %>%
  rename(diet_leaves = leaves, diet_flowers = flowers, diet_seed = seeds, diet_fruit = fruits, diet_inv = arthro, diet_vert = vert,
         diurnal = diu, nocturnal = noc, crepuscular = crepu, bodymass_value = body_mass_g) %>%
  mutate(diet_seed = as.numeric(diet_seed))

amphibio <- amph %>%
  mutate(id = get_ids(species, "itis")) %>%
  filter(!is.na(id)) %>%
  mutate(scientificName = get_names(id, "itis")) %>%
  select(id, scientificName, species) %>%
  right_join(select(amph, -id), by = "species") %>%
  rename(sourceName = species) %>%
  select(-c("order", "family", "genus"))

@@

Select relevant trait columns
```{r}
amphibio <- amphibio %>%
  select(-obs)
```

Check for multiple matches to the same ID
```{r}
amphibio <- undupe_ids(amphibio)
```

### 2019-10-03 data-raw/biotime.Rmd
Also check common names against alternate providers.

@@

#Check for potential matches from synonyms found in the other providers
syn_res <- match_providers(biotime_data, "itis")

>>>>

Many of the studies with only one plot have NA for the plot number, but we want to distinguish between NA's in studies that have multiple plots and unlabled studies.
```{r}
#find studies that only have one plot labeled NA
sing_study <- data %>% 
  select(study_id, plot) %>%
  distinct() %>%
  group_by(study_id) %>%
  count() %>%
  filter(n == 1) %>%
  pull(study_id)

#replace plot NA's that are really studies with only one plot with a plot label 
data <- data %>% 
  mutate(plot = case_when(
    study_id %in% sing_study & is.na(plot) ~ 1,
    TRUE ~ plot
  ))
```

@@

#Check for potential matches from synonyms found in the other providers
syn_res <- match_providers(biotime_data, "itis", common = TRUE)
